Experiment 1 Analysis

### 2023-08-16 Analysis/e1_Analysis.qmd
table updates, analysis approach section

---
title: Experiment 1 Analysis
date: last-modified
categories: [Analysis, R]
page-layout: full
# fig-width: 15
# fig-height: 8
code-fold: true
code-tools: true
toc: false
execute: 
  warning: false
  eval: true
---

```{r setup}
pacman::p_load(tidyverse,lme4,emmeans,here,knitr,kableExtra,gt,gghalves,patchwork,ggforce,ggdist)
e1 <- readRDS(here("data/e1_08-04-23.rds"))
source(here("Functions/Display_Functions.R"))

@@

@@

```{r}
#| tbl-cap: "Mean Vx over blocks. Mean (Standard Error)"
#| tbl-cap-location: top
nb=5
vt1=e1 |> filter(expMode=="train") |>
  learn_curve_table(gt.train,vx,gw=Trial_Bin,groupVec=c(id,vb,condit),nbins=nb,prefix="Block_") |>
  rename("Band"=vb,"Group"=condit)
vt1 %>% kable()

vt1 %>% kable() %>% add_header_above(c(" "," "= 1, "Training Block"=5))

vt1 %>% gt() %>% tab_options(column_labels.background.color = "#176940",
                table.font.size = px(14))

@@

@@

@@

```
### Percent Hit
```{r}

@@

@@

```{r}
#| fig-height: 11
#| fig-width: 12
#| 
rectWidth=.4
vbRect<- e1 %>% group_by(vb) %>% 
  summarise(lowBound=first(bandInt),highBound=first(highBound)) %>% mutate(vbn=as.numeric(vb),
                  vbLag=vbn-rectWidth,vbLead=vbn+rectWidth)

@@

```{r}
#| fig-height: 11
#| fig-width: 12
#| 
sumStats2 = test %>% group_by(id,condit,vb) %>%
  summarise(distMean=mean(dist),distMedian=median(dist),distSd=sd(dist)) %>%group_by(condit,vb) %>%
  summarise(groupMean=round(mean(distMean),0),groupMedian=round(mean(distMedian),0),groupSd=round(mean(distSd),0)) %>%
  mutate(meanLab=paste0("Mean=",groupMean),medianLab=paste0("Median=",groupMedian),sdLab=paste0("Sd=",groupSd)) %>%
  mutate(sumStatLab=paste0(meanLab,"\n",medianLab,"\n",sdLab))

@@

```{r}
#| fig-height: 11
#| fig-width: 12
test %>% group_by(sbjCode,condit,vb) %>% 
  summarise(distMean=mean(dist)) %>% 
  ggplot(aes(x=condit,y=distMean,fill=condit))+
  stat_summary(geom="bar",fun=mean,position=position_nudge(x=.21),alpha=.7,width=.2)+
   stat_summary(geom="errorbar",fun.data=mean_se,position=position_nudge(x=.21),alpha=.7,width=.1,)+
  geom_half_violin(position=position_dodge(.5),alpha=.55,color=NA)+ # remove border color
  geom_half_boxplot(position=position_dodge(.5),side="r",outlier.shape = NA,center=TRUE, 
                    errorbar.draw = FALSE,width=.25,alpha=.55)+
  geom_half_point(transformation = position_jitter(width = 0.05, height = 0.05),alpha=.2,size=.3)+
  facet_wrap(~vb,scale="free_x")+
  scale_y_continuous(expand=expansion(add=200),breaks=round(seq(0,2000,by=200),2))+
  theme(legend.position='none',
        plot.title=element_text(face="bold"),
        axis.title.x=element_text(face="bold"),
        axis.title.y=element_text(face="bold"),
        axis.text.x = element_text(size = 9.0))+
  ylab("Mean Distance From Boundary")+xlab("Training Condition") + 
  ggtitle("Testing Performance (no-feedback) - Absolute Distance from Boundary")+ 
  geom_text(data=sumStats2,aes(y=1390,label = sumStatLab),position=position_dodge(.5),size=3,fontface="bold")

>>>>

---
title: Experiment 1 Analysis
date: last-modified
categories: [Analysis, R]
page-layout: full
# fig-width: 15
# fig-height: 8
toc: false
---

```{r setup, echo=FALSE, include=FALSE}
pacman::p_load(tidyverse,lme4,emmeans,here,knitr,kableExtra,gt,gghalves,patchwork,ggforce,ggdist)
e1 <- readRDS(here("data/e1_08-04-23.rds"))
quietly( source(here::here("Functions", "packages.R")))

@@

```{r}
#| label: test vx table
#| tbl-cap: "Testing - No Feedback"
#| tbl-subcap: ["Constant Testing - X Velocity", "Varied Testing - X Velocity"]
#| layout-ncol: 2
#| echo: fenced

result <- create_summary_table(test, "vx", mfun = list(mean = mean, median = median, sd = sd))
result$constant #|> kable_styling(full_width = F)
result$varied #|> kable_styling(full_width = F)

@@

```{r}
#| tbl-cap: "Mean Vx over blocks. Mean (Standard Error)"
#| tbl-cap-location: top
nb=5
vt1=e1 |> filter(expMode=="train") |>
  learn_curve_table(gt.train,vx,gw=Trial_Bin,groupVec=c(id,vb,condit),nbins=nb,prefix="Block_") |>
  rename("Band"=vb,"Group"=condit)

vt1 %>% kable() %>% add_header_above(c(" "=2, "Training Block "=1," " = ncol(vt1)-3))

# vt1 %>% gt() %>% tab_options(column_labels.background.color = "#176940",
#                 table.font.size = px(14))

@@

# create a kable table to mirror plot of distance effects for vb and condit

e1 |> filter(expMode %in% c("test-Nf","test-train-nf")) |> group_by(vb,condit) %>% 
  summarise(distMean=mean(dist),distSd=sd(dist)) %>% 
  mutate(meanLab=paste0("Mean=",round(distMean,0)),sdLab=paste0("Sd=",round(distSd,0))) %>% 
  mutate(sumStatLab=paste0(meanLab,"\n",sdLab)) %>% 
  select(vb,condit,sumStatLab) %>% 
  spread(condit,sumStatLab) %>% 
  kable(format = "html",escape = FALSE) %>% 
  kable_styling(font_size = 10)

@@

e1 |> filter(expMode %in% c("test-Nf","test-train-nf")) |> group_by(vb,condit) %>% 
  summarise(vxMean=mean(vx),vxSd=sd(vx)) %>% 
  mutate(meanLab=paste0("Mean=",round(vxMean,0)),sdLab=paste0("Sd=",round(vxSd,0))) %>% 
  mutate(sumStatLab=paste0(meanLab,"\n",sdLab)) %>% 
  select(vb,condit,sumStatLab) %>% 
  spread(condit,sumStatLab) %>% 
  kable(format = "html",escape = FALSE) %>% 
  kable_styling(font_size = 10)

@@

e1 |> filter(expMode %in% c("test-Nf","test-train-nf")) |> group_by(vb,condit) %>% 
  summarise(sdistMean=mean(sdist),sdistSd=sd(sdist)) %>% 
  mutate(meanLab=paste0("Mean=",round(sdistMean,0)),sdLab=paste0("Sd=",round(sdistSd,0))) %>% 
  mutate(sumStatLab=paste0(meanLab,"\n",sdLab)) %>% 
  select(vb,condit,sumStatLab) %>% 
  spread(condit,sumStatLab) %>% 
  kable(format = "html",escape = FALSE) %>% 
  kable_styling(font_size = 10)

### Percent Hit
```{r}

@@

testAvg |> group_by(vb,condit) %>% 
  summarise(Percent_HitMean=mean(Percent_Hit),Percent_HitSd=sd(Percent_Hit)) %>% 
  mutate(meanLab=paste0("Mean=",round(Percent_HitMean,3)),sdLab=paste0("Sd=",round(Percent_HitSd,2))) %>% 
  mutate(sumStatLab=paste0(meanLab,"\n",sdLab)) %>% 
  select(vb,condit,sumStatLab) %>% 
  spread(condit,sumStatLab) %>% 
  kable(format = "html",escape = FALSE) %>% 
  kable_styling(font_size = 10)

### Tables

#### BandType

create_table(test, "vx")
create_table(test, "Percent_Hit")

####  Aggregation
```{r}

e1 %>%
  filter(expMode %in% c("test-Nf","test-train-nf")) %>%
  group_by(vb, condit, bandType) %>%
  summarise(distMean = mean(dist), distSd = sd(dist)) %>%
  mutate(
    meanLab = paste0("Mean=", round(distMean, 0)),
    sdLab = paste0("Sd=", round(distSd, 0))
  ) %>%
  mutate(sumStatLab = paste0(meanLab, "\n", sdLab)) %>%
  pivot_wider(
    id_cols = c(vb, bandType),
    names_from = condit,
    values_from = sumStatLab
  ) %>%
  arrange(vb, bandType) %>%
  kable(format = "html", escape = FALSE)

e1 |> filter(expMode %in% c("test-Nf","test-train-nf")) |> group_by(vb,condit) %>% 
  summarise(vxMean=mean(vx),vxSd=sd(vx)) %>% 
  mutate(meanLab=paste0("Mean=",round(vxMean,0)),sdLab=paste0("Sd=",round(vxSd,0))) %>% 
  mutate(sumStatLab=paste0(meanLab,"\n",sdLab)) %>% 
  select(vb,condit,sumStatLab) %>% 
  spread(condit,sumStatLab) %>% 
  kable(format = "html",escape = FALSE,caption = "Vx Mean") %>% 
  kable_styling(font_size = 10)

e1 |> filter(expMode %in% c("test-Nf","test-train-nf")) |> group_by(vb,condit) %>% 
  summarise(sdistMean=mean(sdist),sdistSd=sd(sdist)) %>% 
  mutate(meanLab=paste0("Mean=",round(sdistMean,0)),sdLab=paste0("Sd=",round(sdistSd,0))) %>% 
  mutate(sumStatLab=paste0(meanLab,"\n",sdLab)) %>% 
  select(vb,condit,sumStatLab) %>% 
  spread(condit,sumStatLab) %>% 
  kable(format = "html",escape = FALSE,caption = "Signed Deviation Mean") %>% 
  kable_styling(font_size = 10)

testAvg |> group_by(vb,condit) %>% 
  summarise(Percent_HitMean=mean(Percent_Hit),Percent_HitSd=sd(Percent_Hit)) %>% 
  mutate(meanLab=paste0("Mean=",round(Percent_HitMean,3)),sdLab=paste0("Sd=",round(Percent_HitSd,2))) %>% 
  mutate(sumStatLab=paste0(meanLab,"\n",sdLab)) %>% 
  select(vb,condit,sumStatLab) %>% 
  spread(condit,sumStatLab) %>% 
  kable(format = "html",escape = FALSE,caption = "Mean % Hit") %>% 
  kable_styling(font_size = 10)

#### Tables Aggregating by Id first
```{r}

e1 %>% group_by(id, vb, condit) %>%
  summarise(dist = mean(dist), .groups = 'drop') %>%
  group_by(vb, condit) %>%
  summarise(distMean = mean(dist), distSd = sd(dist), .groups = 'drop') %>%
  mutate(
    meanLab = paste0("Mean=", round(distMean, 0)),
    sdLab = paste0("Sd=", round(distSd, 0))
  ) %>%
  mutate(sumStatLab = paste0(meanLab, "\n", sdLab)) %>%
  select(vb, condit, sumStatLab) %>%
  spread(condit, sumStatLab) %>%
  kable(format = "html", escape = FALSE, caption = "Deviation Mean - Aggregate by Id") %>%
  kable_styling(font_size = 11)

e1 %>%
  filter(expMode %in% c("test-Nf", "test-train-nf")) %>%
  group_by(id, vb, condit) %>%
  summarise(vx = mean(vx), .groups = 'drop') %>%
  group_by(vb, condit) %>%
  summarise(vxMean = mean(vx), vxSd = sd(vx), .groups = 'drop') %>%
  mutate(
    meanLab = paste0("Mean=", round(vxMean, 0)),
    sdLab = paste0("Sd=", round(vxSd, 0))
  ) %>%
  mutate(sumStatLab = paste0(meanLab, "\n", sdLab)) %>%
  select(vb, condit, sumStatLab) %>%
  spread(condit, sumStatLab) %>%
  kable(format = "html", escape = FALSE, caption = "Vx Mean - Aggregate by Id") %>%
  kable_styling(font_size = 11)

e1 %>%
  filter(expMode %in% c("test-Nf", "test-train-nf")) %>%
  group_by(id, vb, condit) %>%
  summarise(sdist = mean(sdist), .groups = 'drop') %>%
  group_by(vb, condit) %>%
  summarise(sdistMean = mean(sdist), sdistSd = sd(sdist), .groups = 'drop') %>%
  mutate(
    meanLab = paste0("Mean=", round(sdistMean, 0)),
    sdLab = paste0("Sd=", round(sdistSd, 0))
  ) %>%
  mutate(sumStatLab = paste0(meanLab, "\n", sdLab)) %>%
  select(vb, condit, sumStatLab) %>%
  spread(condit, sumStatLab) %>%
  kable(format = "html", escape = FALSE, caption = "Signed Distance Mean - Aggregate by Id") %>%
  kable_styling(font_size = 11)

testAvg %>%
  group_by(id, vb, condit) %>%
  summarise(Percent_Hit = mean(Percent_Hit), .groups = 'drop') %>%
  group_by(vb, condit) %>%
  summarise(
    Percent_HitMean = mean(Percent_Hit),
    Percent_HitSd = sd(Percent_Hit),
    .groups = 'drop'
  ) %>%
  mutate(
    meanLab = paste0("Mean=", round(Percent_HitMean, 3)),
    sdLab = paste0("Sd=", round(Percent_HitSd, 2))
  ) %>%
  mutate(sumStatLab = paste0(meanLab, "\n", sdLab)) %>%
  select(vb, condit, sumStatLab) %>%
  spread(condit, sumStatLab) %>%
  kable(format = "html", escape = FALSE, caption = "Mean % Hit - Aggregate by Id") %>%
  kable_styling(font_size = 10)

#### Tables that also indicate bandType
```{r}

# Create the Constant table
constant_table <- e1 %>%
  filter(expMode %in% c("test-Nf", "test-train-nf")) %>%
  group_by(vb, bandType, condit) %>%
  summarise(distMean = mean(dist), distSd = sd(dist)) %>%
  filter(condit == "Constant") %>%
  mutate(
    meanLab = paste0("Mean=", round(distMean, 0)),
    sdLab = paste0("Sd=", round(distSd, 0)),
    sumStatLab = paste0(meanLab, "\n", sdLab)
  ) %>%
  select(vb, bandType, sumStatLab) %>%
  rename(Constant = sumStatLab)

# Create the Varied table
varied_table <- e1 %>%
  filter(expMode %in% c("test-Nf", "test-train-nf")) %>%
  group_by(vb, bandType, condit) %>%
  summarise(distMean = mean(dist), distSd = sd(dist)) %>%
  filter(condit == "Varied") %>%
  mutate(
    meanLab = paste0("Mean=", round(distMean, 0)),
    sdLab = paste0("Sd=", round(distSd, 0)),
    sumStatLab = paste0(meanLab, "\n", sdLab)
  ) %>%
  select(vb, bandType, sumStatLab) %>%
  rename(Varied = sumStatLab)

# Merge tables
final_table <- full_join(constant_table, varied_table, by = "vb")

# Create the table
final_table %>%
  kbl(digits = c(0, 0, 0, 0, 0),
      caption = "Data summary") %>%
  kable_minimal(full_width = FALSE,
      position = "left") %>%
  add_header_above(c("vb" = 1, "Constant" = 2, "Varied" = 2))

@@

```{r}
#| fig-height: 11
#| fig-width: 12
#| eval: false
rectWidth=.4
vbRect<- e1 %>% group_by(vb) %>% 
  summarise(lowBound=first(bandInt),highBound=first(highBound)) %>% mutate(vbn=as.numeric(vb),
                  vbLag=vbn-rectWidth,vbLead=vbn+rectWidth)

@@

```{r}
#| fig-height: 11
#| fig-width: 12
#| eval: false
sumStats2 = test %>% group_by(id,condit,vb) %>%
  summarise(distMean=mean(dist),distMedian=median(dist),distSd=sd(dist)) %>%group_by(condit,vb) %>%
  summarise(groupMean=round(mean(distMean),0),groupMedian=round(mean(distMedian),0),groupSd=round(mean(distSd),0)) %>%
  mutate(meanLab=paste0("Mean=",groupMean),medianLab=paste0("Median=",groupMedian),sdLab=paste0("Sd=",groupSd)) %>%
  mutate(sumStatLab=paste0(meanLab,"\n",medianLab,"\n",sdLab))

@@

```{r}
#| fig-height: 11
#| fig-width: 12
#| eval: false
test %>% group_by(sbjCode,condit,vb) %>% 
  summarise(distMean=mean(dist)) %>% 
  ggplot(aes(x=condit,y=distMean,fill=condit))+
  stat_summary(geom="bar",fun=mean,position=position_nudge(x=.21),alpha=.7,width=.2)+
   stat_summary(geom="errorbar",fun.data=mean_se,position=position_nudge(x=.21),alpha=.7,width=.1,)+
  geom_half_violin(position=position_dodge(.5),alpha=.55,color=NA)+ # remove border color
  geom_half_boxplot(position=position_dodge(.5),side="r",outlier.shape = NA,center=TRUE, 
                    errorbar.draw = FALSE,width=.25,alpha=.55)+
  geom_half_point(transformation = position_jitter(width = 0.05, height = 0.05),alpha=.2,size=.3)+
  facet_wrap(~vb,scale="free_x")+
  scale_y_continuous(expand=expansion(add=200),breaks=round(seq(0,2000,by=200),2))+
  theme(legend.position='none',
        plot.title=element_text(face="bold"),
        axis.title.x=element_text(face="bold"),
        axis.title.y=element_text(face="bold"),
        axis.text.x = element_text(size = 9.0))+
  ylab("Mean Distance From Boundary")+xlab("Training Condition") + 
  ggtitle("Testing Performance (no-feedback) - Absolute Distance from Boundary")+ 
  geom_text(data=sumStats2,aes(y=1390,label = sumStatLab),position=position_dodge(.5),size=3,fontface="bold")
